\begin{practice}{2}{Reuse Robust Component}
\actor{Developers, Senior Developers}
\condition{Mature organization with stable source code and release pipeline. Application performance and maintainability is a big concern for the team.
Developers with higher experience are careful about the quality of the application source code.}
\concern{How can the application avoid boiler plate code and follow best design principles?}
\solution{Use a trusted proven third party library that will keep the code clean and manageable.}
\consideration{The library should be open source, trusted by community, stable and provide apppropriate performance metrics required}
\steps{Find and compare libraries, review thoroughly by more than one developer. Look into the library's source code repository to analyze the stability, quality of the library, and also consider reputed technical blogs.}
\example{So [this large corporation] as a whole is actually built on the open source libraries that are suitable for our use cases. But that actually has been one of our primary focus as well. If you find a library, use it; only build if you can’t find anything.}{P13}
\end{practice}

% \begin{table}[]
%     \centering
%     \caption{Scenario of GP2: Reuse Robust Component}
%     \begin{tabular}{p{1cm}p{7.5cm}}
%          \toprule
%             \textbf{GP} & \textbf{Reuse Robust Component} \\ 
%             \midrule
%             Actor(s) & Developers, Senior Developers \\ 
%             Context & - Matured organization with stable source code and release pipeline. Application performance and maintainability is a big concern for the team.
%             - Developers with higher experience would be careful about the quality of the application source code. \\ 
%             Concern & How the application can avoid boiler plate code and follow best design principles? \\ 
%             Solution & Use a trusted proven third party library that will keep the code clean and manageable. \\ 
%             Consider-ation & The library should be open source, trusted by community, stable and provide apppropriate performance metrics required \\ 
%             Steps & Find and compare libraries, review thoroughly by more than one developer. \\ 
%             Support & Look into the library's source code repository to analyze the stability, quality of the library, and also consider reputed technical blogs. \\ 
%             Example Trace in Data & So [this large corporation] as a whole is actually built on the open source libraries that are suitable for our use cases. But that actually has been one of our primary focus as well. If you find a library, use it; only build if you can’t find anything. (P13) \\ 
%          \bottomrule
%     \end{tabular}
%     \label{tab:gp2-scenario}
% \end{table}