\begin{practice}{4}{Empower the Team}
\actor{Developers, Tech Leaders}
\condition{Some organizations may have a strong company culture to improve the development skill set or for providing comfortable learning space for developers. 
Tech leaders may care more for their team's capacity, limitations, and motivations.
The development team may have limitations or strengths in certain technologies. }
\concern{Does the library fit well with the capability of the development team? Will it provide them any transferable skills?}
\solution{Use a library that is appreciated by the developers}
\consideration{The library should be well documented and should have a popular community so that developers can easily adopt and can refer in future. Also it can have customer support in case developers needs extra help.}
\steps{Besides finding a library that fits well with the technology, thoroughly discuss with developers about their opinion and acceptance of the library. Look into official documentation of the library for documentation and support issues.}
\example{So looking at community popularity helps because then it helps to hire people. It helps to retain people. They like to use technologies that are transferable.}{P19}
\end{practice}


% \begin{table}[]
%     \centering
%     \caption{Scenario of GP4: Empower the Team}
%     \begin{tabular}{p{1cm}p{7.5cm}}
%          \toprule
%             \textbf{GP} & \textbf{Empower the Team} \\ 
%             \midrule
%             Actor(s) & Developers, Tech Leaders \\ 
%             Context & - Some organizations may have strong company culture to improve development skill set or for providing comfortable learning space for developers. 
%             - Tech leaders may care more for their team's capacity, limiatation, and motivation.
%             - Development team may have limitation or strength in certain technology  \\ 
%             Concern & Does the library fit well with the capability of the development team? Will it provide them any transferable skill? \\ 
%             Solution & Use a library that is appreciated by the developers \\ 
%             Consider-ation & Library should be well documented, should be community popular so that developers can easily adopt and can refer in future. Also it can have customer support in case developers needs extra help. \\ 
%             Steps & Besides finding a library that fits well with the technology, thoroughly discuss with developers about their opinion and acceptance of the library. \\ 
%             Support & Look into official documentation of the library for documentation and support issues. \\ 
%             Example Trace in Data & So looking at community popularity helps because then you can it helps to hire people. It helps to retain people. They like to use technologies that are transferable (P19) \\ 
%          \bottomrule
%     \end{tabular}
%     \label{tab:gp4-scenario}
% \end{table}